Wealth Inequality in China: Evidence from the 2017 and 2019 CHFS

### 2025-04-20 report/draft.qmd
update

---
title: "Wealth Inequality in China: Evidence from the 2017 and 2019 CHFS"
format:
    pdf:
        documentclass: article 
        author: Chenning Xu
        number-sections: true
        margin-top: 1in
        margin-bottom: 1in
        margin-left: 1in
        margin-right: 1in
        linestretch:  1.2
        fontsize: 10pt
    html: default    
bibliography: tom.bib
---

@@

| Statistic | Income 2011 | Income 2017 | Income 2019 | Wealth 2011 | Wealth 2017 | Wealth 2019 |
|-----------|-------------|-------------|-------------|-------------|-------------|-------------|
| Mean      | 60,053     | 89,634     | 94,005     | 687,061    | 839,008    | 1,085,589    |
| Median    | 28,312     | 54,108     | 57,035     | 197,150    | 322,515    | 457,600    |
| Gini      | 0.664      | 0.605      | 0.614     | 0.761      | 0.701      | 0.667      |
| N         | 8,438      | 38,994     | 33,387     | 8,438      | 38,994     | 33,387     |

@@

| 2017 Wealth      | Gini Correlation | Gini Coefficient | Share   | Contribution |
|-------------------|------------------|------------------|---------|--------------|
| Housing Equity  | 0.9610          | 0.7244          | 0.6996  | 0.6950       |
| Land Asset      | 0.4722          | 0.9204          | 0.0392  | 0.0243       |
| Commercial Equity | 0.8246          | 1.1989          | 0.0667  | 0.0941       |
| Commercial Property | 0.8290          | 0.9890          | 0.0213  | 0.0250       |
| Car Equity        | 0.6648          | 0.9037          | 0.0339  | 0.0290       |
| Financial Equity  | 0.8022          | 0.7964          | 0.1232  | 0.1123       |
| Other Equity      | 0.6485          | 0.9438          | 0.0213  | 0.0186       |
| Educational Debt  | -0.3166         | 0.9846          | 0.0014  | -0.0006      |
| Credit Card Debt  | 0.3678          | 0.9899          | 0.0015  | 0.0008       |
| Medical Debt      | -0.5801         | 0.9786          | 0.0023  | -0.0018       |

| 2019 Wealth      | Gini Correlation | Gini Coefficient | Share   | Contribution |
|-------------------|------------------|------------------|---------|--------------|
| Housing Equity  | 0.9591          | 0.7015          | 0.6834  | 0.6876       |
| Land Asset      | 0.7155          | 0.9700          | 0.0593  | 0.0615       |
| Commercial Equity | 0.6812          | 1.2014          | 0.0359  | 0.0440       |
| Commercial Property | 0.7778          | 0.9886          | 0.0144  | 0.0166       |
| Car Equity        | 0.6651          | 0.8224          | 0.0344  | 0.0281       |
| Financial Equity  | 0.7895          | 0.7484          | 0.1532  | 0.1354       |
| Other Equity      | 0.7171          | 1.0296          | 0.0224  | 0.0247       |
| Educational Debt  | -0.4199         | 0.9885          | 0.0008  | -0.0005      |
| Credit Card Debt  | 0.3029          | 0.9854          | 0.0012  | 0.0005       |
| Medical Debt      | -0.5591         | 0.9844          | 0.0016  | -0.0014       |

@@

| Group      | Sample Share | Mean    | Relative Mean | Median Income | Wealth Share | Gini |
|------------|--------------|---------|---------------|---------------|--------------|------|
| 2017 Urban | 0.6235 | 1,146,510 | 1.3665 | 66,760 | 0.8521 | 0.6573 |
| 2017 Rural | 0.3765 | 329,715 | 0.3930 | 23,660 | 0.1479 | 0.6945 |
| 2019 Urban | 0.6500 | 1,461,675 | 1.3464 | 69,600 | 0.8752 | 0.6165 |
| 2019 Rural | 0.3500 | 387,130 | 0.3566 | 27,541 | 0.1248 | 0.6629 |

@@

| Year | Total Gini | Within-group | Between-group | Residual |
|------|------------|--------------|---------------|----------|
| 2017 | 100.00 | 55.35 | 32.61 | 12.04 |
| 2019 | 100.00 | 56.79 | 33.68 | 9.53 |

@@

| Region         | Sample Share | Mean        | Relative Mean | Median Income | Wealth Share | Gini   |
|----------------|--------------|-------------|---------------|---------------|--------------|--------|
| 2017 East     | 0.3754       | 1,391,421   | 1.6584        | 556,993       | 0.6226       | 0.6747 |
| 2017 Middle   | 0.2659       | 550,976     | 0.6567        | 272,235       | 0.1746       | 0.6648 |
| 2017 West     | 0.2628       | 496,937     | 0.5923        | 252,341       | 0.1556       | 0.6569 |
| 2017 Northeast| 0.0960       | 412,387     | 0.4915        | 212,512       | 0.0472       | 0.6513 |
| 2019 East     | 0.3987       | 1,658,323   | 1.5276        | 760,140       | 0.6090       | 0.6305 |
| 2019 Middle   | 0.2651       | 677,697     | 0.6243        | 372,434       | 0.1655       | 0.5997 |
| 2019 West     | 0.2400       | 799,535     | 0.7365        | 343,542       | 0.1768       | 0.6947 |
| 2019 Northeast| 0.0962       | 549,715     | 0.5064        | 291,085       | 0.0487       | 0.6369 |

@@

The decomposition of the Gini coefficient into within-group, between-group, and residual components shows:

| Year | Total Gini | Within-group | Between-group | Residual |
|------|------------|--------------|---------------|----------|
| 2017 | 100.00 | 31.16 | 36.88 | 31.96 |
| 2019 | 100.00 | 31.69 | 33.77 | 34.54 |

@@

>>>>

---
title: "Wealth Inequality in China: Evidence from the 2017 and 2019 CHFS"
format: 
    pdf:
        documentclass: article 
        number-sections: true
        margin-top: 1in
        margin-bottom: 1in
        margin-left: 1in
        margin-right: 1in
        linestretch:  1.2
        fontsize: 10pt
        fig-pos: "H"
        author: "Chenning Xu"
bibliography: tom.bib
---

@@

::: {#tbl-tbl1}

{{< include summary_stats.txt >}}

Source: @tan_earnings_2017's calculation based on the 2011 CHFS data and authors' calculation based on the 2017 and 2019 CHFS data.

Mean, Median, and Gini Coefficient for Income and Wealth in China, 2011, 2017, and 2019
:::

@@

::: {#tbl-tbl2}

{{< include 2017_gini_decom.txt >}}

Source: Author's calculation based on the 2017 CHFS data.

Decomposition of Wealth Gini Coefficient by Urban-Rural Division, 2017
:::

::: {#tbl-tbl3}

{{< include 2019_gini_decom.txt >}}

Source: Author's calculation based on the 2019 CHFS data.

Decomposition of Wealth Gini Coefficient by Urban-Rural Division, 2019
:::

@@

::: {#tbl-tbl4}

{{< include rural_urban_summary.txt >}}

Source: Author's calculation based on the 2017 and 2019 CHFS data.

Summary Statistics of Urban and Rural Income and Wealth, 2017 and 2019
:::

@@

::: {#tbl-urbanrural-decomp}

{{< include urban_rural_gini_decomp.txt >}}

Source: Author's calculation based on the 2017 and 2019 CHFS data.

Decomposition of Wealth Gini Coefficient by Urban-Rural Division, 2017 and 2019 (%)
:::

@@

::: {#tbl-region-summary}

{{< include region_summary.txt >}}

Source: Author's calculation based on the 2017 and 2019 CHFS data.

Summary Statistics by Region, 2017 and 2019
:::

@@

::: {#tbl-region-decomp}

{{< include region_gini_decomp.txt >}}

Source: Author's calculation based on the 2017 and 2019 CHFS data.

Decomposition of Wealth Gini Coefficient by Region, 2017 and 2019 (%)
:::

@@

## What's next
I will read more papers and contrast the results with data in this study. I am not sure about what else I can do for this paper. I would like to hear your suggestions. Thanks.
